openarchaeoCollaboration

### 2022-04-25 analysis/paper.Rmd
Note or fix some errors preventing knit

```{r plot-lifespan-hist}
oarch_lifespan %>%
  ggplot(aes(x = lifespan)) +
  geom_histogram(binwidth = 100) +
  scale_x_continuous(breaks = scales::breaks_width(1000)) +
  labs(
    title = "Project lifespan",
    subtitle = "Time between first and latest commit, by repository",
    x = "Days", y = NULL,
    caption = "Data: open-archaeo.info and GitHub API"
  ) +
  theme_oarch()

@@

```{r plot-contrib-dist}
oarch %>%
  unnest(gh_contribs) %>%
  drop_na(contributor) %>%
  group_by(item_name) %>%
  mutate(n_contributors = n()) %>%
  filter(n_contributors > 1) %>%
  mutate(big_boy = ifelse(contributions == max(contributions),
                          "Main contributor", "Other contributors"),
         big_boy_pct = max(contributions) / sum(contributions)) ->x %>%
  ggplot(aes(x = fct_reorder(item_name, big_boy_pct, .desc = FALSE),
             y = contributions,
             # group = contributor,
             fill = fct_relevel(big_boy, c("Other contributors",
                                           "Main contributor")))) +
  geom_col(position = "fill", colour = "white", size = 0.1) +
  scale_y_continuous(labels = scales::percent) +
  scale_fill_contrast(guide = guide_legend(reverse = TRUE)) +
  labs(title = "Repository contributors by proportion of contributions",
       x = NULL, y = "Contributions",
       fill = NULL,
       caption = "Data: open-archaeo.info and GitHub API") +
  coord_flip() +
  theme_oarch() +
  theme(
    axis.text.y = element_blank(),
    axis.ticks.y = element_blank()
  )

@@

```{r plot-lifespan-activity-tags}
left_join(oarch_lifespan, oarch, by = c("item_name")) %>%
  pivot_longer(c(tag1, tag2, tag3, tag4, tag5), values_to = "tag",
               values_drop_na = TRUE) %>%
  drop_na(tag) %>%
  group_by(tag) %>%
  summarise(avg_lifespan = mean(lifespan),
            avg_commit_rate = mean(commit_rate)) ->
  oarch_lifespan_by_tag

>>>>

```{r plot-lifespan-hist}
# TODO: where does oarch_lifespan come from?
oarch_lifespan %>%
  ggplot(aes(x = lifespan)) +
  geom_histogram(binwidth = 100) +
  scale_x_continuous(breaks = scales::breaks_width(1000)) +
  labs(
    title = "Project lifespan",
    subtitle = "Time between first and latest commit, by repository",
    x = "Days", y = NULL,
    caption = "Data: open-archaeo.info and GitHub API"
  ) +
  theme_oarch()

@@

```{r plot-contrib-dist}
oarch %>%
  unnest(gh_contribs) %>%
  drop_na(contributor) %>%
  group_by(item_name) %>%
  mutate(n_contributors = n()) %>%
  filter(n_contributors > 1) %>%
  mutate(big_boy = ifelse(contributions == max(contributions),
                          "Main contributor", "Other contributors"),
         big_boy_pct = max(contributions) / sum(contributions)) %>%
  ggplot(aes(x = fct_reorder(item_name, big_boy_pct, .desc = FALSE),
             y = contributions,
             # group = contributor,
             fill = fct_relevel(big_boy, c("Other contributors",
                                           "Main contributor")))) +
  geom_col(position = "fill", colour = "white", size = 0.1) +
  scale_y_continuous(labels = scales::percent) +
  scale_fill_highcontrast(guide = guide_legend(reverse = TRUE)) +
  labs(title = "Repository contributors by proportion of contributions",
       x = NULL, y = "Contributions",
       fill = NULL,
       caption = "Data: open-archaeo.info and GitHub API") +
  coord_flip() +
  theme_oarch() +
  theme(
    axis.text.y = element_blank(),
    axis.ticks.y = element_blank()
  )

@@

```{r plot-lifespan-activity-tags}
# TODO: where does oarch_lifespan come from?
left_join(oarch_lifespan, oarch, by = c("item_name")) %>%
  pivot_longer(c(tag1, tag2, tag3, tag4, tag5), values_to = "tag",
               values_drop_na = TRUE) %>%
  drop_na(tag) %>%
  group_by(tag) %>%
  summarise(avg_lifespan = mean(lifespan),
            avg_commit_rate = mean(commit_rate)) ->
  oarch_lifespan_by_tag
